Solution of near-Toeplitz tridiagonal systems on GPU-accelerated clusters

### 2016-03-24 paper-draft/paper.tex
Changes to section justifying the use of cyclic reduction

\usepackage{amsmath,bm}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{minted}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{rotating}

@@

\hl{
Thus, cyclic reduction requires \emph{significantly} fewer steps
($2log_2(n) - 1$) compared to Thomas algorithm ($2n$).
Each step in cyclic reduction consists of operations on several indices
that can each be done in parallel,
making it a good fit for massively parallel architectures such as GPUs.}

@@

First, we note that
the secondary systems
[Eq. (\ref{eqn:secondary-system-1-expanded}) and
 Eq. (\ref{eqn:secondary-system-2-expanded})]
are dependent only on $\bm{a}$, $\bm{b}$ and $\bm{c}$,
the tridiagonal coefficients of the global tridiagonal system.
\hl{These are the same for all local grid lines,
so they are \emph{precomputed} -
solved \emph{once} for a single local grid line in each subdomain.
This is done on the CPU.}

>>>>

\usepackage{amsmath,bm}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{minted}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{rotating}
\soulregister\cite{7}

@@

\hl{
Although the total number of operations involved in cyclic reduction ($17n$)
is larger compared to the Thomas algorithm ($8n$),
cyclic reduction requires \emph{significantly} fewer steps
($2log_2(n) - 1$) compared to Thomas algorithm ($2n$) \cite{Zhang2010FTS}.
At each step, the operations at each index in cyclic reduction
can be done independently,
making it amenable to parallel solution.
Further, when solving multiple tridiagonal systems with different right hand sides,
cyclic reduction exposes a larger degree of parallelism
than solving the systems using a thread-parallel Thomas algorithm.
This fact, along with a more favourable memory access pattern,
has made cyclic reduction---and the
closely related \emph{parallel cyclic reduction} algorithm---the
basis for most approaches to solving tridiagonal systems on GPUs \cite{chang2014guide}.
}

@@

First, we note that
the secondary systems
[Eq. (\ref{eqn:secondary-system-1-expanded}) and
 Eq. (\ref{eqn:secondary-system-2-expanded})]
are dependent only on $\bm{a}$, $\bm{b}$ and $\bm{c}$,
the tridiagonal coefficients of the global tridiagonal system.
\hl{These are the same for all local grid lines,
so they are \emph{precomputed} -
solved \emph{once} for a single local grid line in each subdomain.}
